Confidence Intervals for Prevalence Estimates from Complex Surveys with Imperfect Assays

### 2021-11-01 PrevAdjSurvey.tex
Updates from Overleaf

\author[2]{Michael P. Fay*}

@@

\authormark{D. M. BAYER, M.P. FAY and B. I. Graubard \textsc{et al}}

@@

\address[2]{\orgdiv{Department of Statistics}, \orgname{University of California, Irvine}, \orgaddress{\state{Irvine, California}, \country{Country name}}}

@@

@@

@@

Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial parameter.
For each of these, we use distributions associated with  the exact binomial confidence interval.
For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).

@@

\begin{equation}
    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
\end{equation}

@@

\begin{equation}
    B^L_{CP} \sim \operatorname{Binomial}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
\end{equation}

\begin{equation}
    B^U_{CP} \sim \operatorname{Binomial}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
\end{equation}

with \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.

@@

\label{sec:weight-imperfect}

\section{Results}
\subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}
\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}

@@

@@

THERE IS A SMALL ERROR IN THESE RESULTS. RERUNNING ON BIOWULF NOW. I DON'T EXPECT THE SUBSTANCE TO CHANGE.

@@

\begin{itemize}
    \item For sharing the data from the Kalish, et al study, we thank Matthew Memoli and the LID Clinical Studies Unit of the National Institute of Allergy and Infectious Diseases, NIH,  Kaitlyn Sadtler from the National Institute of Biomedical Imaging and Bioengineering, NIH,   Matthew Hall from the National Center for Advancing Translational Sciences, NIH, and Dominic Esposito from the Fredrick National Laboratory for Cancer Research, NCI, NIH.
    \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation. I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.  
    \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.  For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%). 
\end{itemize}

\section{Introduction}\label{sec1}

Many authors submitting \( \sin \cos \tan \inf_{x} \) to NJD journals use \LaTeXe\ to
prepare their papers. This paper describes the
\textsf{WileyNJD-v2.cls} class file which can be used to convert
articles produced with other \LaTeXe\ class files into the correct
form for publication in \emph{Wiley NJD Journals}.

The \textsf{WileyNJD-v2.cls} class file preserves much of the standard
\LaTeXe\ interface so that any document which was produced using
the standard \LaTeXe\ \textsf{article} style can easily be
converted to work with the \textsf{WileyNJD-v2} style. However, the
width of text and typesize will vary from that of
\textsf{article.cls}; therefore, \emph{line breaks will change}
and it is likely that displayed mathematics and tabular material
will need re-setting.

In the following sections we describe how to lay out your code to
use \textsf{WileyNJD-v2.cls} to reproduce the typographical look of
\emph{Wiley NJD Journals}.

\subsection{Procedure to install fonts (not required on Overleaf)}

\begin{enumerate}
\item All font files are available under the Stix-fonts folder in the zip download at \url{https://onlinelibrary.wiley.com/page/journal/10991476/homepage/latex_class_files.htm}
\item Font installer is available under the same folder Windows-Stix-fontinstaller.exe
\item Execute (double click the EXE file) the EXE file that will install all fonts/map files to your local drive.
\end{enumerate}

\subsection{The Three Golden Rules}

Before we proceed, we would like to
stress \emph{three golden rules} that need to be followed to
enable the most efficient use of your code at the typesetting
stage:
\begin{enumerate}
\item[(i)] keep your own macros to an absolute minimum;

\item[(ii)] as \TeX\ is designed to make sensible spacing
decisions by itself, do \emph{not} use explicit horizontal or
vertical spacing commands, except in a few accepted (mostly
mathematical) situations, such as \verb"\," before a
differential~d, or \verb"\quad" to separate an equation from its
qualifier;

\item[(iii)] follow the \emph{NJD} reference style.
\begin{enumerate}[a.]
\item Chemistry --- Use the ``AMA'' option as \verb"\documentclass[AMA]{WileyNJD-v2.cls}"

\end{enumerate}
\end{enumerate}

\section{Getting Started} The \textsf{WileyNJD-v2.cls} class file should run
on any standard \LaTeXe\ installation. If any of the fonts, class
files or packages it requires are missing from your installation,
they can be found on the \emph{\TeX\ Live} CD-ROMs or from CTAN.

LaTeX document class options

\begin{flushleft}
\begin{enumerate}[a.]
\item STIX1COL--- For STIX font large one column layout use the ``STIX1COL'' option as \verb"\documentclass[AMA,STIX1COL]{WileyNJD-v2}"
\item STIX2COL--- For STIX font large two column layout use the ``STIX2COL'' option as \verb"\documentclass[AMA,STIX2COL]{WileyNJD-v2}"
\item STIXSMALL--- For STIX font small layout use the ``STIXSMALL'' option as \verb"\documentclass[AMA,STIXSMALL]{WileyNJD-v2}"
\end{enumerate}
\end{flushleft}

\section{The Article Header Information}
The heading for any file using \textsf{WileyNJD-v2.cls} is shown in
Figure~\ref{F1}.

\subsection{Remarks}

\begin{enumerate}[(I).]

\item Use \verb"\title{<title> \protect\thanks{<title footnotes}}" for article title and title footnote.
\item Use \verb"\authormark{}" for running heads.

\item Note the use of \verb"\author[<link>]{<name>}" and \verb"\address[<link>]{<name>}" to
link names and addresses. The author for correspondence is marked
by ``*'' and \verb"\corres{}" is used to give that
author's address, which will be printed besides abstract, prefaced by
`Correspondence to:'.

\item For submitting a double-spaced manuscript, add
\verb"doublespace" as an option to the documentclass line. \verb"\documentclass[doublespace]{WileyNJD-v2}"

\item Use \verb"\presentaddress{}" for present address.

\item In abstract \verb"\abstract[<title>]{abstract paragraph}" use optional parameter for title followed by abstract paragraph.

\item For Key words use \verb"\keywords{}".

\item For how to site use \verb"\jnlcitation{\cname{\author{<author name>},"

\verb"\ctitle{<title>}, \cjournal{<Journal name>}, \cvol{<vol>}.}}".

\item For title page abbreviations use \verb"\footnotetext{<\textbf{Abbreviation title:} Abreviations>}"

\item Use \verb"\articletype{<article category}" for article header information

\item Use \verb"\received{<received date>} \revised{<revised date>} \accepted{<accepted date>}" for history dates.

\end{enumerate}

\begin{figure}[p]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}

\documentclass[AMA,STIX1COL]{WileyNJD-v2}

\received{26 April 2016}
\revised{6 June 2016}
\accepted{6 June 2016}

\title{<Initial cap, lower case>\protect\thanks{<title footnote.>}}

\author[<address link>]{<Author name><corresponding author*>}

\author[<address link>,<address link>]{Author Name}

\authormark{AUTHOR ONE \textsc{et al}}

\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>}, 
\orgaddress{\state{<State name>}, \country{<Country name>}}}
\address[<address link>]{\orgdiv{<Org Division>}, \orgname{<Org name>},
 \orgaddress{\state{<State name>}, \country{<Country name>}}}

\corres{<corresponding author link*> <author name, address.
 \email{<authorone@email.com>}}

\presentaddress{<Present address>}

\abstract[<Abstract heading>]{<Abstract paragraph>}

\keywords{<keyword1>, <keyword2>,...}

\jnlcitation{\cname{%
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>}, 
\author{<aurhor name>},  and 
\author{<aurhor name>}} (\cyear{<year>}), 
\ctitle{<journal title>}, \cjournal{<journal name>} <year> <vol> Page <xxx>-<xxx>}

\footnotetext{\textbf{<abbreviation head:>} <abbreviations> ..}

\section{Introduction}
.
.
.
\end{boxedverbatim}
\end{center}
\caption{Example for title page.\label{F1}}
\end{figure}

\section{The Body of the Article}

\subsection{Section headings}

\begin{enumerate}[(H1)]
\item Section --- use \verb"\section{}"
\item SubSection--- use \verb"\subsection{}"
\item SubSubSectioin--- use \verb"\subsubsection{}"
\item Paragraph--- use \verb"\paragraph{}"
\item Subparagraph--- use \verb"\subparagraph{}"
\end{enumerate}

\subsection{Mathematics} \textsf{WileyNJD-v2.cls} makes the full
functionality of \AmS\/\TeX\ available. We encourage the use of
the \verb"align", \verb"gather" and \verb"multline" environments
for displayed mathematics.

\subsection{Figures and Tables}

\textsf{WileyNJD-v2.cls} uses the
\textsf{graphicx} package for handling figures.

Figures are called in as follows:
\begin{verbatim}
\begin{figure}
\centering
\includegraphics{<figure name>}
\caption{<Figure caption>}
\end{figure}
\end{verbatim}

The standard coding for a table is shown in Figure~\ref{F2}.

\begin{figure}[h]
\setlength{\fboxsep}{0pt}%
\setlength{\fboxrule}{0pt}%
\begin{center}
\begin{boxedverbatim}
\begin{table}
\caption{<Table caption>}
\centering
\begin{tabular}{<table alignment>}
\toprule
<column headings>\\
\midrule
<table entries
(separated by & as usual)>\\
<table entries>\\
.
.
.\\
\bottomrule
\end{tabular}
\begin{tablenotes}
\item Source: xxx.
\item[1] xxx.
\item[2] xxx.
\end{tablenotes}
\end{table}
\end{boxedverbatim}
\end{center}
\caption{Example for table layout.\label{F2}}
\end{figure}

\subsection{Cross-referencing}
The use of the \LaTeX\ cross-reference system
for figures, tables, equations, etc., is encouraged
(using \verb"\ref{<name>}" and \verb"\label{<name>}").

\subsection{Box text}

\begin{verbatim}
\begin{boxtext}
\section*{<title>}%
Paragraph
\end{boxtext}
\end{verbatim}

\subsection{List items}

\subsubsection{Enumerate list styles}
\begin{verbatim}
\begin{enumerate}[1]
\item 
\end{enumerate}

\begin{enumerate}[1.]
\item 
\end{enumerate}

\begin{enumerate}[(1)]
\item 
\end{enumerate}

\begin{enumerate}[I]
\item 
\end{enumerate}

\begin{enumerate}[i]
\item 
\end{enumerate}

\begin{enumerate}[a]
\item 
\end{enumerate}

\end{verbatim}

\subsubsection{Bullet list styles}

\begin{verbatim}
\begin{itemize}
\item 
\end{itemize}
\end{verbatim}

\subsubsection{Description list}

\begin{verbatim}
\begin{description}
\item[<entry>] description text.
\end{description}
\end{verbatim}

\subsection{Enunciations}

\begin{verbatim}
\begin{theorem}[<Theorem subhead>]\label{thm1}
<theorem text>. 
\end{theorem}

\begin{proposition}[<proposition subhead>]\label{pro1}
<proposition text>. 
\end{proposition}

\begin{definition}[<definition subhead>]\label{dfn1}
<definition text>. 
\end{definition}

\begin{proof}
<proof text>. 
\end{proof}

\begin{proof}[Proof of Theorem~\ref{thm1}]
<proof text>.
\end{proof}

\end{verbatim}

\subsection{Program codes}

Use \verb+\begin{verbatim}...\end{verbatim}+ for program codes without math. Use \verb+\begin{alltt}...\end{alltt}+ for program codes with math. Based on the text provided inside the optional argument of \verb+\begin{code}[Psecode|Listing|Box|Code|+\hfill\break \verb+Specification|Procedure|Sourcecode|Program]...+ \verb+\end{code}+ tag corresponding boxed like floats are generated. Also note that \verb+\begin{code}[Code|Listing]...+ \verb+\end{code}+ tag with either Code or Listing text as optional argument text are set with computer modern typewriter font.  All other code environments are set with normal text font. Refer below example:

\begin{verbatim}
\begin{lstlisting}[caption={Descriptive Caption Text},label=DescriptiveLabel]
for i:=maxint to 0 do
begin
{ do nothing }
end;
Write('Case insensitive ');
WritE('Pascal keywords.');
\end{lstlisting}
\end{verbatim}

\subsection{Acknowledgements} An Acknowledgements section is started with \verb"\ack" or
\verb"\acks" for \textit{Acknowledgement} or
\textit{Acknowledgements}, respectively. It must be placed just
before the References.

\subsection{Bibliography}
% \nocite{*}% Show all bib entries - both cited and uncited; comment this line to view only cited bib entries;
% \bibliography{WileyNJD-AMA}%
\begin{enumerate}[1]
\item Use \verb"\bibliography{wileyNJD-AMA}" BST file for AMA reference style
\item Use \verb"\bibliography{wileyNJD-APA}" BST file for APA reference style
\item Use \verb"\bibliography{wileyNJD-AMS}" BST file for AMS reference style
\item Use \verb"\bibliography{wileyNJD-VANCOUVER}" BST file for Vancouver reference style
\item Use \verb"\bibliography{wileyNJD-ACS}" BST file for Chemistry reference style
\end{enumerate}

The normal commands for producing the reference list are:

\begin{verbatim}
\begin{thebibliography}{99}
\bibitem{<x-ref label>}
         <Reference details>
.
.
.
\end{thebibliography}
\end{verbatim}

\subsection{Appendix Section}

\begin{verbatim}
\appendix

\section{Section title of first appendix\label{app1}}
.
.
.

\end{verbatim}

>>>>

\author[1]{Michael P. Fay*}

@@

\authormark{D. M. BAYER, M.P. FAY and B. I. GRAUBARD \textsc{et al}}

@@

\address[2]{\orgdiv{Department of Statistics}, \orgname{University of California, Irvine}, \orgaddress{\state{Irvine, California}}}

@@

\section{To Do List}
\begin{itemize}
    \item Write abstract
    \item Write introduction
    \item Write discussion
    \item Figure revisions:
    \begin{itemize}
        \item Part 1: Rename "Fay" to "Melding"?
        \item Part 1: Increase font size
        \item Part 2: Rename Clopper-Pearson to Korn-Graubard
        \item Part 3: Replace simulations results with corrected results (still running on Biowulf)
    \end{itemize}
    \item Fix acknowledgements \LaTeX
    \item Fix bibiliogrpahy \LaTeX
\end{itemize}

@@

and the apparent prevalence is

\begin{equation}
    \beta = \frac{\sum_{i=1}^k N_i \theta_i}{\sum_{j=1}^k N_j} = \sum_{i=1}^k w_i \theta_i,
    \label{eq:app-prev}
\end{equation}

@@

Each estimated component in Equation~\ref{eq:srs-beta-est} is a binomial probability parameter.
For each of these, we use distributions associated with  the exact binomial confidence interval.
For a binomial experiment with \( x \) successes out of \( n \) trials, the lower confidence distribution \( (B^L) \) is \( \operatorname{Beta}(x, n - x + 1) \), and the upper confidence distribution \( (B^U) \) is \( \operatorname{Beta}(x + 1, n - x)\).

@@

\begin{equation}
    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{\theta_1}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{\theta_1}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
\label{eq:srs-conf-int}
\end{equation}

@@

\begin{equation}
    % B^L_{CP} \sim \operatorname{Beta}\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i, n_{\text{eff}} \left(1 -  \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1\right)
    B^L_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}},  n_{\text{eff}} -  x_{\text{eff}} + 1 \right)
\end{equation}

\begin{equation}
    % B^U_{CP} \sim \operatorname{Beta}\left(\left(n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i\right) + 1, n_{\text{eff}} \left(1 - \sum_{i=1}^k w_i \hat{\theta}_i \right)\right)
    B^U_{CP} \sim \operatorname{Beta}\left(x_{\text{eff}} + 1, n_{\text{eff}} - x_{\text{eff}} \right)
\end{equation}

with \( x_{\text{eff}} = n_{\text{eff}} \sum_{i=1}^k w_i \hat{\theta}_i \), and \( n_{\text{eff}} \) defined in Equation~\ref{eq:neff}.

@@

Lastly, we develop a confidence interval for the population prevalence, \( \beta^* \), in the case where \( k > 1 \), \( \phi_n > 0 \), \( \phi_p < 1 \).

The two methods we discuss are closely related to each other and the methods discussed in Sections~\ref{sec:srs-imperfect} and \ref{sec:weight-perfect}.
As in Section~\ref{sec:srs-imperfect}, we use the melding method \cite{FayP:2015} to create \( a \)\% confidence interval very similar to Equation~\ref{eq:srs-conf-int}.
The confidence distributions for \( \phi_p \) and \( \phi_n \) are the same Beta distributions as in Section~\ref{sec:srs-imperfect}.
The two methods differ in their confidence distributions for the apparent prevalence \( \beta \).

In the first case, we use the adaptation of \cite{FayF:1997} presented in Section~\ref{sec:weight-perfect} to derive the \( a \)\% confidence interval for \( \beta^* \):

\begin{equation}
    \left\{ q \left( \frac{1 - a}{2}, \frac{G_{\beta}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{G_{\beta}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
\end{equation}

where \( G_{\beta}^L \) and \( G_{\beta}^U \) are the same as \( G_{\beta^*}^L \) and \( G_{\beta^*}^U \) as defined in Section~\ref{sec:weight-perfect}.

The alternative method is that used in \cite{Kali:2021}.
We use the  modification of \cite{Korn:1998} presented in \cite{Dean:2015}, as in Section~\ref{sec:weight-perfect}, to derive the \( a \)\% confidence interval for \( \beta^* \):

\begin{equation}
    \left\{ q \left( \frac{1 - a}{2}, \frac{B_{CP}^L + B_{\phi_n}^L }{B_{\phi_p}^U + B_{\phi_n}^L }  \right),  q \left( \frac{1 + a}{2}, \frac{B_{CP}^U + B_{\phi_n}^U}{B_{\phi_p}^L + B_{\phi_n}^U}  \right) \right\}.
\end{equation}

where \( B_{CP}^L \) and \( B_{CP}^U \) are as defined in Section~\ref{sec:weight-perfect}.

\section{Results}

\subsection{Estimating Prevalence from a Simple Random Sample with an Imperfect Assay}

We assess and compare our new method (Fay) to that of Lang and Reiczigel (LR) in a variety of simulated settings.
In each simulation, 100 subjects are tested to estimate prevalence, 60 are tested to estimate sensitivity, and 300 are tested to estimate specificity.
Several combinations of prevalences (0.5\%--2\%), sensitivities (75\%--100\%) and specificities (75\%--100\%) are assessed.
Each simulated scenario is replicated 10,000 times.
Figure~\ref{fig:coverage_comparison_plot} compares the two methods based on coverage, while Figures~\ref{fig:lower_error_frequency_comparison_plot} and \ref{fig:upper_error_frequency_comparison_plot} present the lower and upper error frequencies for these scenarios, respectively.

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/coverage_comparison_plot}
    \caption{Coverage properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
    \label{fig:coverage_comparison_plot}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/lower_error_frequency_comparison_plot}
    \caption{Lower error properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
    \label{fig:lower_error_frequency_comparison_plot}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\textwidth]{figures/upper_error_frequency_comparison_plot}
    \caption{Upper error properties for our new method (Fay) and the state of the art method (LR) in a variety of settings, each simulated 10,000 times.}
    \label{fig:upper_error_frequency_comparison_plot}
\end{figure}

\subsection{Estimating Prevalence from a Weighted Sample with a Perfect Assay}

We compare the wsPoisson method to the more traditional Agresti-Coull and Korn-Graubard methods in a variety of settings.
Our simulations examine varying levels of disease prevalence (0.5\% or 5\%), types of groups surveyed (50 groups 200 subjects or 8000 groups of 1 subject), distributions of weights among the groups (coefficient of variation from 0-6), the number of groups with non-zero prevalence, and the weights of the groups with non-zero prevalence.
For each scenario, 10,000 data sets are simulated and assessed.

The coverage properties for these simulations are presented in Figures~\ref{fig:perfect_coverage_50_0_005_reduced}--\ref{fig:perfect_coverage_8000_0_05_reduced.pdf}.

@@

\subsection{Estimating Prevalence from a Weighted Sample with an  Imperfect Assay}
\todo[inline]{THERE IS A SMALL ERROR IN THE SIMULATION RESULTS. RERUNNING ON BIOWULF NOW. I DON'T EXPECT THE SUBSTANCE TO CHANGE.}

We also apply these two methods to a real data set from \cite{Kali:2021}.
This data set was collected to estimate seroprevalence of SARS-CoV-2 in the United States between May and July 2020.
First we apply the methods to the full data set (\( n =  8058, \text{weight coefficient of variation} = "252\%\)).
The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.53\%, 6.68\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.56\%, "7.54\%).

We also apply the methods to the subset of only hispanic participants (\( n = 1281, \text{weight coefficient of variation} = 306\% \)).
The Korn and Graubard type confidence distributions produce the 95\% confidence interval for population prevalence (2.35\%, 11.75\%), while the wsPoisson type confidence distributions produce the 95\% confidence interval (2.40\%, 20.02\%).

\begin{itemize}
    \item The last time we met, you mentioned that it would be nice to report the weights in terms of coefficient of variation. I went back to the data from the COVID seroprevalence paper in undiagnosed adults, and I calculated a coefficient of variation  of 2.52 = 252\% for all 8058 individuals, and looking at subsets, I found that the Hispanics had a CV=306\%.  
    \item For some weighting for surveys to adjust for selection bias, the coefficient of variation may be large.  For example, the coefficient of variation of the weights (CVW) for the main estimate of seroprevalence in Kalish, et al (2021) had CVW=252\%, and it could be even larger for subsets of the population (e.g., Hispanics had CVW=306\%). 
\end{itemize}

\acks
\begin{acks}
For sharing the data from the Kalish, et al study, we thank Matthew Memoli and the LID Clinical Studies Unit of the National Institute of Allergy and Infectious Diseases, NIH,  Kaitlyn Sadtler from the National Institute of Biomedical Imaging and Bioengineering, NIH,   Matthew Hall from the National Center for Advancing Translational Sciences, NIH, and Dominic Esposito from the Fredrick National Laboratory for Cancer Research, NCI, NIH.
\end{acks}

\appendix
\section{Additional Figures}

@@

@@
